---
output:
  word_document: default
  html_document: default
---
# EIPS variables: Formulations and distributions {#variables}

```{r setup, include=FALSE, echo=FALSE}
if(!require("gt")){install.packages("gt");  library(gt)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}
if(!require("openxlsx")){install.packages("openxlsx");  library(openxlsx)}
if(!require("webshot")){install.packages("webshot");  library(webshot)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE)
```


This chapter displays tables with distributions for each variable included in the survey, as well as question wordings and values for each individual panel.

## NORDFORSK1

Could you please now imagine that an incident has taken place in the Nordic region and then consider some questions about the incident below.
The incident involves a *[tactic1]* that targeted *[target]* [on Iceland / in Norway / in Sweden]. 
*[Casualties]* were killed in *[tactic2]*, which was performed by *[perpetrator]*  *[actor type*. 
News coverage suggests *[motivation]*.

```{r conjoint_dim}

tactic1 <- tibble(Source = c('protest', 'sabotage', 'hostage taking', 'shooting', 'bombing'),
                  Iceland = c('Mótmæli áttu', 'Skemmdarverk áttu', 'Gíslataka átti', 'Skotárás átti', 'Sprengjuárás átti'),
                  Norway = c('protest', 'sabotasje', 'gisseltaking', 'skyting', 'bombing'),
                  Sweden = c('En protest', 'En skjutning',)
)
                  
                  
                target = c('a military facility', 'a police station', 'a school', 'a church', 'a mosque', 'a synagogue'),
                casualties = c('No one', 'One person', 'Two people', 'Ten people'),
                tactic2 = c('the protest', 'the sabotage', 'the hostage taking', 'the shooting', 'the bombing'),
                perpetrator = c('one', 'one Christian', 'one Muslim', 'one left-wing extremist', 'one right-wing extremist'),
                type = c('organisation', 'group', 'individual', 'individual of unsound mind'),
                motivation = c('there was no clear motivation behind the incident', 'the incident was carried out with the aim of changing government policy', 'the motivation behind the incident came from a hatred towards the target')
)

                
                
                
                

```
## EIPS2017E

>We are interested in how people see the role of referendums in political decisions. Imagine a debate surfaced concerning the membership of [*PANEL COUNTRY*] in the EU, and that an advisory referendum was held on the issue.  

>[EIPS2017E_turnout]   

>[EIPS2017E_winner]   

>[EIPS2017E_majoritysize]    

>[EIPS2017E_dv]   


*Translations*

France: Nous souhaiterions savoir le rôle qu’attribuent les citoyens aux référendums dans les décisions politiques. Imaginez qu’un grand débat soit ouvert concernant l’adhésion de la France à l’U.E. et que la question soit soumise à un référendum de consultation. 

Germany: "Wir würden gerne wissen, wie die Menschen über die Rolle von Volksbefragungen (unverbindliche Referenden) bei politischen Entscheidungen denken. Stellen Sie sich vor, es kommt zu einer Diskussion über die EU-Mitgliedschaft von Deutschland und einer Volksbefragung in dieser Frage.  "

Iceland: "Við höfum áhuga á að sjá hvert fólk telur hlutverk þjóðaratkvæðagreiðslna í pólitískri ákvarðanatöku. Ímyndaðu þér að umæður væru um aðild Íslands að Evrópusambandinu og að leiðbeinandi þjóðaratkvæðagreiðsla væri haldin um málið." 

Netherlands:  Wij zijn geïnteresseerd in meningen over de rol van referenda in het politieke besluitvormingsproces. Stelt u zich voor dat er een debat ontstaat over het Nederlandse lidmaatschap van de EU en dat hierover een raadgevend referendum wordt gehouden.

Norway: "Vi er interesserte i hvordan innbyggerne vurderer folkeavstemningers rolle i politiske beslutninger. Se for deg at det kom en ny debatt vedrørende norsk medlemskap i EU, og at det ble holdt en rådgivende folkeavstemning om saken. "

Sweden:  Vi är intresserade av hur människor ser betydelsen av folkomröstningar i politiska beslut. Föreställ dig att en debatt tog fart om Sveriges medlemskap i EU, och att en rådgivande folkomröstning hölls i frågan.  



### EIPS2017E_dv

>What is right in such a situation, should the government follow the outcome of the referendum even though the majority of the national parliament disagreed with the referendum outcome?

France:  Dans une telle situation, estimez-vous que le gouvernement doit se plier aux résultats du référendum même si la majorité parlementaire nationale est d’un avis contraire?

Germany: "Welche Reaktion wäre in diesem Fall angemessen? Sollte sich die Regierung an das Ergebnis der Volksbefragung halten, auch dann, wenn die Mehrheit des Bundestags dagegen wäre?"

Iceland: "Hvað er rétt að gera í þessum aðstæðum, eiga stjórnvöld að fara að niðurstöðu þjóðaratkvæðagreiðslunnar jafnvel þó meirihluti þingmanna á þinginu væri ósammála niðurstöðum hennar?"

Netherlands:  Wat is in een dergelijke situatie correct: moet de regering de uitkomst van het referendum overnemen, zelfs als de meerderheid van het parlement het niet met de uitkomst van het referendum eens is?

Norway: "Hva mener du er riktig i et slikt tilfelle, burde regjeringen følge resultatet i folkeavstemningen selv om flertallet i Stortinget er uenig?"

Sweden: Vad är rätt i en sådan situation, bör regeringen följa folkomröstningens resultat trots att majoriteten av det nationella parlamentet inte höll med om folkomröstningens resultat?

```{r }
kable(EIPS2017E_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>%
  footnote(general = "Variable names. France = pe03_EIPS2017E, Germany = ZH29054, Iceland = EIPS2017E_dv, Netherlands = EIPS2017E & EIPS2017Echeck, Norway = eips2017e_dv, Sweden = EIPS2017E_dv")

kable(EIPS2017E_q, 'latex', booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values, Post-treatment measure",  col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>%
  kable_styling(latex_options = 'scale_down') %>% 
  footnote(general = "Variable names. France = pe03_EIPS2017E, Germany = ZH29054, Iceland = EIPS2017E_dv, Netherlands = EIPS2017E & EIPS2017Echeck, Norway = eips2017e_dv, Sweden = EIPS2017E_dv") %>% 
  cat(., file = here("output", "tbl-EIPS2017E_q.html"))
  
```

```{r }
kable(EIPS2017E, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) 

kable(EIPS2017E, 'latex', booktabs = T, linesep = "", escape = F, caption = "Distributions, Post-treatment measure", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  kable_styling(latex_options = 'scale_down') %>% 
  cat(., file = here('output', 'tbl-EIPS2017E.html'))
```

### EIPS2017E_turnout

```{r }

kable(EIPS2017E_turnout_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017E_TURNOUT, Germany = expZH29054_1, Iceland = EIPS2017E_turnout, Netherlands = EIPS2017E_turnout, Norway = eips2017e_turnout, Sweden = EIPS2017E_turnout")

kable(EIPS2017E_turnout_q, 'latex', booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values, Turnout treatment", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  kable_styling(latex_options = 'scale_down') %>% 
    footnote(general = "Variable names : France = pe03_EIPS2017E_TURNOUT, Germany = expZH29054_1, Iceland = EIPS2017E_turnout, Netherlands = EIPS2017E_turnout, Norway = eips2017e_turnout, Sweden = EIPS2017E_turnout") %>% 
  cat(., file = here('output', 'tbl-EIPS2017E_turnout_q.html'))
```

```{r }

kable(`EIPS2017E_turnout (RV)`, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))

kable(`EIPS2017E_turnout (RV)`,'latex', booktabs = T, linesep = "", escape = F, caption = "Distributions:Turnout treatment", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  kable_styling(latex_options = 'scale_down') %>% 
  cat(., file = here('output', 'tbl-EIPS2017E_turnout.html'))
```

### EIPS2017E_majoritysize

```{r }

kable(EIPS2017E_majoritysize_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "*Variable names:** France = pe03_EIPS2017E_MAJORITYSIZE, Germany = expZH29054_2, Iceland = EIPS2017E_majoritysize, Netherlands = EIPS2017E_majoritysize, Norway = eips2017e_majoritysize, Sweden = EIPS2017E_majoritysize")

kable(EIPS2017E_majoritysize_q, 'latex', booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values: 
      Majority size treatment", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  kable_styling(latex_options = 'scale_down') %>% 
  footnote(general = "*Variable names:** France = pe03_EIPS2017E_MAJORITYSIZE, Germany = expZH29054_2, Iceland = EIPS2017E_majoritysize, Netherlands = EIPS2017E_majoritysize, Norway = eips2017e_majoritysize, Sweden = EIPS2017E_majoritysize") %>%
  cat(., file = here('output', 'tbl-EIPS2017E_majoritysize_q.html'))

```

```{r }

kable(`EIPS2017E_majoritysize (RV)`, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(number = "The Icelandic survey programmed only two values on this variable -- *Not shown* and *51 percent*, which explains the larger number of observations for these values in the Iceland and total EIPS samples.")

kable(`EIPS2017E_majoritysize (RV)`, 'latex', booktabs = T, linesep = "", escape = F, caption = "Distributions: Majority size treatment", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  kable_styling(latex_options = 'scale_down') %>% 
  footnote(number = "The Icelandic survey programmed only two values on this variable -- *Not shown* and *51 percent*, which explains the larger number of observations for these values in the Iceland and total EIPS samples.") %>% 
  cat(., file = here('output', 'tbl-EIPS2017E-majoritysize.html'))
```

### EIPS2017E_winner

```{r }

kable(EIPS2017E_winner_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017E_WINNER, Germany = expZH29054_3, Iceland = EIPS2017E_winner, Netherlands = EIPS2017E_winner, Norway = eips2017e_winner, Sweden = EIPS2017E_winner")

kable(EIPS2017E_winner_q, 'latex', booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values: Winner treatment", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  kable_styling(latex_options = 'scale_down') %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017E_WINNER, Germany = expZH29054_3, Iceland = EIPS2017E_winner, Netherlands = EIPS2017E_winner, Norway = eips2017e_winner, Sweden = EIPS2017E_winner") %>% 
  cat(., file = here('output', 'tbl-EIPS2017E_winner_q.html'))
```

```{r }

kable(`EIPS2017E_winner (RV)`, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) 

kable(`EIPS2017E_winner (RV)`, 'latex', booktabs = T, linesep = "", escape = F, caption = "Distributions: Winner treatment", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  cat(., file = here('output', 'tlb-EIPS2017E_winner.html'))

```

## EIPS2017F

> How much would you say that the political system in [EIPS2017F_entity] allows people like you to have an influence on politics?

*Translations*

France: Dans quelle mesure estimez-vous que le système politique actuel en [EIPS2017F_entity] permet aux citoyens d’exercer une influence réelle sur les décisions politiques ?

Germany: Aus Ihrer Sicht: In welchem Maße gibt das politische System in [EIPS2017F_entity] Menschen wie Ihnen die Möglichkeit, Einfluss auf die Politik zu nehmen?   

Iceland: Að hversu miklu leyti telur þú að stjórnmálakerfið á [EIPS2017F_entity] leyfi fólki eins og þér tækifæri á að hafa áhrif á stjórnmál?   

Netherlands: In hoeverre stelt het politieke systeem in [EIPS2017F_entity] mensen zoals u in staat invloed uit te oefenen op de politiek?

Norway: I hvilken grad vil du si at det politiske systemet i [EIPS2017F_entity] gir folk som deg innflytelse på det myndighetene gjør?  

Sweden:  Hur mycket skulle du säga att det politiska systemet i Sverige gör det möjligt för människor som du att påverka politiken?


### EIPS2017F_dv

```{r }
kable(EIPS2017F_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))%>%
  footnote(general = "Variable names. France = pe03_EIPS2017F, Germany = ZH29055, Iceland = EIPS2017F_dv, Netherlands = EIPS2017F & EIPS2017Fcheck, Norway = eips2017f_dv, Sweden = EIPS2017F_dv")
```

```{r }

kable(EIPS2017A, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) 
```

### EIPS2017F_entity
```{r }

kable(EIPS2017F_entity_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017F_ENTITY, Germany = expZH29055, Iceland = EIPS2017F_entity, Netherlands = EIPS2017F_entity, Norway = eips2017f_dv, Sweden = EIPS2017F_entity")
```

```{r }

kable(`EIPS2017F_entity (RV)`, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

## EIPS2017G

>Below we describe two hypothetical political candidates.  Please read the descriptions of each person carefully. 
>
|  | Candidate 1  | Candidate 2   |
|--------------|----------------|------------------------------|
| Gender  |  [EIPS2017G_1_gender] |  [EIPS2017G_2_gender] |
| Age  | [EIPS2017G_1_age]  | [EIPS2017G_2_gender] |
| Completed education  | [EIPS2017G_1_edu]  | [EIPS2017G_2_edu] |
| Religion    |  [EIPS2017G_1_religion] |  [EIPS2017G_2_religion] |
| Family background  | [EIPS2017G_1_class]  |  [EIPS2017G_2_class] |

>[EIPS2017G_1_dv] or [EIPS2017G_2_dv]

*Translations*

France: Deux candidats politiques fictifs sont présentés ci-dessous. Veuillez lire avec attention la description de chacune de ces deux personnalités.

Germany: Nachfolgend stellen wir Ihnen zwei mögliche politische Kandidaten oder Kandidatinnen vor. Bitte lesen Sie sich die Profile der folgenden Personen sorgfältig durch.  

Iceland: Hér að neðan lýsum við tveimur ímynduðum frambjóðendum til kosninga. Vinsamlega lestu lýsinguna á hvorri persónu vandlega.  

Netherlands:  Hieronder worden twee denkbeeldige politieke kandidaten beschreven. Lees de beschrijvingen aandachtig door.

Norway: I tabellen under beskriver vi to tenkte politiske kandidater. Vennligst les beskrivelsen av hver person nøye.   

Sweden: Nedan beskriver vi två hypotetiska politiska kandidater.  Läs varje persons beskrivning noggrant.

- Note: In this conjoint experiment, the German Internet Panel randomly assigned respondents into groups before the conjoint table randomization, while the other panels did it after. Therefore, there are double sets of variables for the treatment dimensions. These have been merged in the distributions tables.


### EIPS2017G_1_dv

> Based on your own judgment, please indicate which political candidate you think will agree most with your own political views.

*Translations*

France: Veuillez indiquer le candidat politique qui reflète le mieux vos opinions politiques. 

Germany: Bitte geben Sie an, welcher der beiden politischen Kandidaten oder Kandidatinnen Ihrer Meinung nach am ehesten Ihre politischen Ansichten teilt.  

Iceland: Að þínu mati, hvor frambjóðandinn telur þú að sé meira sammála þínum eigin  stjórnmálaskoðunum?  

Netherlands:  Based on your own judgment, please indicate which political candidate you think will agree most with your own political views.

Norway: Ut fra din egen vurdering, hvilken politisk kandidat tror du vil være mest enig med dine politiske standpunkter?  

Sweden: Utifrån din egen bedömning, ange vilken politisk kandidat du tycker passar dina politiska åsikter bäst.

```{r }
kable(EIPS2017G_1_dv_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))%>%
  footnote(general = "Variable names. France = pe03_EIPS2017G_1_DV, Germany = ZH29056, Iceland = EIPS2017G_1_dv, Netherlands = EIPS2017G1 & EIPS2017G1check, Norway = eips2017g_2, Sweden = EIPS2017G_1_dv")
```

```{r }
kable(EIPS2017G_1_dv, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

### EIPS2017G_2_dv

> Relying solely on this information, which political candidate would you prefer as your political representative at the national level?

*Translations*

France:  D’après les informations données, quel candidat politique préféreriez-vous en tant que représentant politique au niveau national ?

Germany: Wenn Sie nur die Angaben aus den Profilen berücksichtigen: Welche dieser zwei Personen würden Sie als Ihren politischen Vertreter oder Ihre politische Vertreterin auf Bundesebene bevorzugen?   

Iceland: Ef þú styðst eingöngu við þessar upplýsingar,  hvorn frambjóðandann vildir þú frekar sem þinn fulltrúa á Alþingi?  

Netherlands:  Welke politieke kandidaat zou u, uitsluitend op basis van deze informatie, op nationaal niveau als uw politieke vertegenwoordiger willen zien?  

Norway: Dersom du kun skulle basere deg på denne informasjonen, hvilken politisk kandidat ville du ha foretrukket som din politiske representant på Stortinget?

Sweden:  Enbart utifrån denna information, vilken politisk kandidat skulle du föredra som din politiska representant på nationell nivå?

```{r }
kable(EIPS2017G_2_dv_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))%>%
  footnote(general = "Variable names. France = pe03_EIPS2017G_2_DV, Germany = ZH29057, Iceland = EIPS2017G_2_dv, Netherlands = EIPS2017G2 & EIPS2017G2check, Norway = eips2017g_2, Sweden = EIPS2017G_2_dv")
```

```{r}

kable(EIPS2017G_2_dv, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) 
```


###Gender of political candidates

#### EIPS2017G_1_gender

>Candidate 1

```{r }
kable(EIPS2017G_1_gender_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017G_C1_GENDER, Germany = ZH29056_1 & ZH29057_1, Iceland = EIPS2017G_1_gender, Netherlands = EIPS2017G_1_gender, Norway = eips2017g_1_gender, Sweden = EIPS2017G_1_gender")

```

```{r }
kable(EIPS2017G_1_gender, booktabs = T, linesep = "", escape = F, caption = "Distributions", 
col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017G_2_gender

Candidate 2

```{r }
kable(EIPS2017G_2_gender_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))%>% 
  footnote(general = "Variable names : France = pe03_EIPS2017G_C2_GENDER, Germany = ZH29056_2 & ZH29057_2, Iceland = EIPS2017G_2_gender, Netherlands = EIPS2017G_2_gender, Norway = eips2017g_2_gender, Sweden = EIPS2017G_2_gender")
```

```{r}
kable(EIPS2017G_2_gender,  booktabs = T, linesep = "", escape = F, caption = "Distributions candidate 2", 
col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

### Age of political candidates

####EIPS2017G_1_age

>Candidate 1

```{r }
kable(EIPS2017G_1_age_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "**Variable names: France = pe03_EIPS2017G_C1_AGE, Germany = ZH29056_3 & ZH29057_3, Iceland = EIPS2017G_1_age, Netherlands = EIPS2017G_1_age, Norway = eips2017g_1_age, Sweden = EIPS2017G_1_age")
```

```{r}

kable(EIPS2017G_1_age,  booktabs = T, linesep = "", escape = F, caption = "Distributions", 
col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017G_2_age

>Candidate 2

```{r }
kable(EIPS2017G_1_age_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017G_C2_AGE, Germany = ZH29056_4 & ZH29057_4, Iceland = EIPS2017G_2_age, Netherlands = EIPS2017G_2_age, Norway = eips2017g_2_age, Sweden = EIPS2017G_2_age")
```

```{r}

kable(EIPS2017G_2_age, booktabs = T, linesep = "", escape = F, caption = "Distributions", 
col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

###Education levels of political candidates

#### EIPS2017G_1_edu

>Candidate 1

```{r }
kable(EIPS2017G_1_edu_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017G_C1_EDU, Germany = ZH29056_5 & ZH29057_5, Iceland = EIPS2017G_1_edu, Netherlands = EIPS2017G_1_edu, Norway = eips2017g_1_edu, Sweden = EIPS2017G_1_edu")
```

```{r}
kable(EIPS2017G_1_edu,  booktabs = T, linesep = "", escape = F, caption = "Distributions", 
col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```


#### EIPS2017G_2_edu

>Candidate 2

```{r }
kable(EIPS2017G_2_edu_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017G_C2_EDU, Germany = ZH29056_6 & ZH29057_6, Iceland = EIPS2017G_2_edu, Netherlands = EIPS2017G_2_edu, Norway = eips2017g_2_edu, Sweden = EIPS2017G_2_edu")
```

```{r}

kable(EIPS2017G_2_edu,  booktabs = T, linesep = "", escape = F, caption = "Distributions", 
col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

###Family background of political candidates

#### EIPS2017G_1_class

>Candidate 1

```{r }
kable(EIPS2017G_1_class_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017G_C1_CLASS, Germany = ZH29056_9 & ZH29057_9, Iceland = EIPS2017G_1_class, Netherlands = EIPS2017G_1_class, Norway = eips2017g_1_class, Sweden = EIPS2017G_1_class")
```

```{r}

kable(EIPS2017G_1_class,  booktabs = T, linesep = "", escape = F, caption = "Distributions", 
col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017G_2_class

>Candidate 2

```{r }
kable(EIPS2017G_2_class_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names:** France = pe03_EIPS2017G_C2_CLASS, Germany = ZH29056_10 & ZH29056_10, Iceland = EIPS2017G_2_class, Netherlands = EIPS2017G_2_class, Norway = eips2017g_2_class, Sweden = EIPS2017G_2_class")
```

```{r}

kable(EIPS2017G_2_class,  booktabs = T, linesep = "", escape = F, caption = "Distributions", 
col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

### Religion of political candidates

#### EIPS2017G_1_religion

>Candidate 1

```{r }
kable(EIPS2017G_1_religion_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017G_C2_RELIGION, Germany = ZH29056_7 & ZH29057_7, Iceland = EIPS2017G_1_religion, Netherlands = EIPS2017G_1_religion, Norway = eips2017g_1_religion, Sweden = EIPS2017G_1_religion")
```

```{r}

kable(EIPS2017G_1_religion,  booktabs = T, linesep = "", escape = F, caption = "Distributions", 
col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017G_2_religion

>Candidate 2

```{r }
kable(EIPS2017G_2_religion_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017G_C2_RELIGION, Germany = ZH29056_8 & ZH29057_8, Iceland = EIPS2017G_2_religion, Netherlands = EIPS2017G_2_religion, Norway = eips2017g_2_religion, Sweden = EIPS2017G_2_religion")
```

```{r}

kable(EIPS2017G_2_religion,  booktabs = T, linesep = "", escape = F, caption = "Distributions", 
col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```



## EIPS2017H
 
The respondents see a table with two political candidates that have randomly varying attributes (such as age and gender). The experiment has two post measures, which are presented in random order to the respondents below the table with the candidate description. H_1 and H_2 only differ with respect to question ordering.  

### EIPS2017H_1

>Below we describe two hypothetical political candidates.  Please read the descriptions of each person carefully. 
>
|  | Candidate 1  | Candidate 2   |
|--------------|----------------|------------------------------|
| Gender  |  [EIPS2017H_1_gender] |  [EIPS2017H_1_gender] |
| Age  | [EIPS2017H_1_age]  | [EIPS2017H_1_gender] |
| Completed education  | [EIPS2017H_1_edu]  | [EIPS2017H_1_edu] |
| Family background  | [EIPS2017H_1_class]  |  [EIPS2017H_1_class] |
| Main occupational background    |  [EIPS2017H_1_occupation] |  [EIPS2017H_1_occupation] |
| Experience in political office  |  [EIPS2017H_1_polex] |  [EIPS2017H_1_polex] |
| Lived and worked past 5 years  |  [EIPS2017H_1_workplace] |  [EIPS2017H_1_workplace] |
| Recent editorial in main quality newspaper  |  [EIPS2017H_1_media] |  [EIPS2017H_1_media] |
| Political ideology  |  [EIPS2017H_1_ideology] |  [EIPS2017H_1_ideology] |
| Immigration view  |  [EIPS2017H_1_immigration] |  [EIPS2017H_1_immigration] |
| EU membership view  |  [EIPS2017H_1_eumembership] |  [EIPS2017H_1_eumembership] |  

>*Either:*  
1. [EIPS2017H_1a]: If there were national elections tomorrow and you had to vote for one of these two candidates, which candidate would you choose?

>2. [EIPS2017H_1b] : Which candidate is in your view most likely to represent the concerns of ordinary people in your contry?

>*Or:*

>1. [EIPS2017H_2a]: Which candidate is in your view most likely to represent the concerns of ordinary people in your country?  
>2. [EIPS2017H_2b]: If there were national elections tomorrow and you had to vote for one of these two candidates, which candidate would you choose? 


#### EIPS2017H_1a

```{r }
kable(EIPS2017H_1a_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))%>%
  footnote(general = "Variable names. France = pe03_EIPS2017H_1_DV1, Germany = ZH29058, Iceland = EIPS2017H_1_dv1, Netherlands = EIPS2017H11 & EIPS2017H11check, Norway = eips2017h_1a, Sweden = EIPS2017H_1_dv1")
```

```{r}

kable(EIPS2017H_1a, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) 
```

#### EIPS2017H_1b

```{r }
kable(EIPS2017H_1b_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))%>%
  footnote(general = "Variable names. France = pe03_EIPS2017H_1_DV2, Germany = ZH29059, Iceland = EIPS2017H_1_dv2, Netherlands = EIPS2017H12 & EIPS2017H12check, Norway = eips2017h_1b, Sweden = EIPS2017H_1_dv2")
```

```{r}

kable(EIPS2017H_1b, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) 
```


#### EIPS2017H_2a

```{r }
kable(EIPS2017H_2a_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))%>%
  footnote(general = "Variable names. France = pe03_EIPS2017H_2_DV1, Germany = ZH29060, Iceland = EIPS2017H_1_dv1, Netherlands = EIPS2017H21 & EIPS2017H21check, Norway = eips2017h_2a, Sweden = EIPS2017H_1_dv1")
```

```{r}

kable(EIPS2017H_2a, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) 
```

#### EIPS2017H_2b

```{r }
kable(EIPS2017H_2b_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))%>%
  footnote(general = "Variable names. France = pe03_EIPS2017H_2_DV2, Germany = ZH29061, Iceland = EIPS2017H_2_dv2, Netherlands = EIPS2017H22 & EIPS2017H22check, Norway = eips2017h_2b, Sweden = EIPS2017H_1_dv2")
```

```{r}

kable(EIPS2017H_2b, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) 
```


#### EIPS2017H_1_gender

> >Candidate 1's gender

```{r}
kable(EIPS2017H_1_gender_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C1_GENDER, Germany = ZH29058_1 & ZH29060_1, Iceland = EIPS2017H_1_gender_1 & EIPS2017H_2_gender_1, Netherlands = EIPS2017H_1_gender, Norway = eips2017h_1_gender, Sweden = EIPS2017H_1_gender")
```

```{r}
kable(EIPS2017H_1_gender, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017H_2_gender

>Candidate 2's gender

```{r}
kable(EIPS2017H_2_gender_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C2_GENDER, Germany = ZH29058_2 & ZH20060_2, Iceland = 
EIPS2017H_1_gender_2 & EIPS2017H_2_gender_2, Netherlands = EIPS2017H_2_gender, Norway = eips2017h_2_gender, Sweden = EIPS2017H_2_gender")
```

```{r}
kable(EIPS2017H_2_gender, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```


#### EIPS2017H_1_age

>Candidate 1's age

```{r}
kable(EIPS2017H_1_age_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C1_AGE, Germany = ZH29058_3 & ZH29060_3, Iceland = EIPS2017H_1_age_1 & EIPS2017H_2_age_1, Netherlands = EIPS2017H_1_age, Norway = eips2017h_1_age, Sweden = EIPS2017H_1_age")
```

```{r}
kable(EIPS2017H_1_age, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017H_2_age

>Candidate 2's age

```{r}
kable(EIPS2017H_2_age_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C2_AGE, Germany = ZH29058_4 & ZH29060_4, Iceland = EIPS2017H_1_age_2 & EIPS2017H_2_age_2, Netherlands = EIPS2017H_2_age, Norway = eips2017h_2_age, Sweden = EIPS2017H_2_age")
```

```{r}
kable(EIPS2017H_2_age, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017H_1_edu

>Candidate 1's level of education

```{r}
kable(EIPS2017H_1_edu_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C1_EDU, Germany = ZH29058_5 & ZH20060_5, Iceland = EIPS2017H_1_edu_1 & EIPS2017H_2_edu_1, Netherlands = EIPS2017H_1_edu, Norway = eips2017h_1_edu, Sweden = EIPS2017H_1_edu")
```

```{r}
kable(EIPS2017H_1_edu, booktabs = T, linesep = "", escape = F,  caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017H_2_edu

>Candidate 2's level of education

```{r}
kable(EIPS2017H_2_edu_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C2_EDU, Germany = ZH29058_6 & ZH20060_6, Iceland = EIPS2017H_1_edu_2 & EIPS2017H_2_edu_2, Netherlands = EIPS2017H_2_edu, Norway = eips2017h_2_edu, Sweden = EIPS2017H_2_edu")
```

```{r}
kable(EIPS2017H_2_edu, booktabs = T, linesep = "", escape = F,  caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden"))) 
```

#### EIPS2017H_1_class

>Candidate 1's family background (class)

```{r}
kable(EIPS2017H_1_class_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C1_CLASS, Germany = ZH29058_7 & ZH20060_7, Iceland = EIPS2017H_1_class_1 & EIPS2017H_2_class_1, Netherlands = EIPS2017H_1_class, Norway = eips2017h_1_class, Sweden = EIPS2017H_1_class")
```

```{r}
kable(EIPS2017H_1_class, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden"))) 
```

#### EIPS2017H_2_class

>Candidate 2's family background (class)

```{r}
kable(EIPS2017H_2_class_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C2_CLASS, Germany = ZH29058_8 & ZH20060_8, Iceland = EIPS2017H_1_class_2 & EIPS2017H_2_class_2, Netherlands = EIPS2017H_2_class, Norway = eips2017h_2_class, Sweden = EIPS2017H_2_class")
```

```{r}
kable(EIPS2017H_2_class, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017H_1_occupation

>Candidate 1's work experience outside politics

```{r}
kable(EIPS2017H_1_occupation_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C1_OCCUPATION, Germany = ZH29058_9 & ZH20060_9, Iceland = EIPS2017H_1_occupation_1 & EIPS2017H_2_occupation_1, Netherlands = EIPS2017H_1_occupation, Norway = eips2017h_1_occupation, Sweden = EIPS2017H_1_occupation")
```

```{r}
kable(EIPS2017H_1_occupation, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden"))) 
```

#### EIPS2017H_2_occupation

>Candidate 2's work experience outside politics

```{r}
kable(EIPS2017H_2_occupation_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names:** France = pe03_EIPS2017H_C2_OCCUPATION, Germany = ZH29058_10 & ZH20060_10, Iceland = EIPS2017H_1_occupation_2 & EIPS2017H_2_occupation_2, Netherlands = EIPS2017H_2_occupation, Norway = eips2017h_2_occupation, Sweden = EIPS2017H_2_occupation")
```

```{r}
kable(EIPS2017H_2_occupation, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany ",	"Iceland", "Netherlands", "Norway", "Sweden"))) 
```

#### EIPS2017H_1_polex

>Political experience of candidate 1

```{r}
kable(EIPS2017H_1_polex_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C1_POLEX, Germany = ZH29058_12 & ZH20060_12, Iceland = EIPS2017H_1_polex_1 & EIPS2017H_2_polex_1, Netherlands = EIPS2017H_1_polex, Norway = eips2017h_1_polex, Sweden = EIPS2017H_1_polex")
```

```{r}
kable(EIPS2017H_1_polex, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017H_2_polex

>Political experience of candidate 2

```{r}
kable(EIPS2017H_2_polex_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C2_POLEX, Germany = ZH29058_12 & ZH20060_12, Iceland = EIPS2017H_1_polex_2 & EIPS2017H_2_polex_2, Netherlands = EIPS2017H_2_polex, Norway = eips2017h_2_polex, Sweden = EIPS2017H_2_polex")
```

```{r}
kable(EIPS2017H_2_polex, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017H_1_workplace

>Candidate 1's workplace

```{r}
kable(EIPS2017H_1_workplace_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C1_WORKPLACE, Germany = ZH29058_13 & ZH20060_13, Iceland = EIPS2017H_1_workplace_1 & EIPS2017H_2_workplace_1, Netherlands = EIPS2017H_1_workplace, Norway = eips2017h_1_workplace, Sweden = EIPS2017H_1_workplace")
```

```{r}
kable(EIPS2017H_1_workplace, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland ",	"Netherlands", "Norway", "Sweden")))
```

#### EIPS2017H_2_workplace

>Candidate 2's workplace

```{r}
kable(EIPS2017H_2_workplace_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C2_WORKPLACE, Germany = ZH29058_14 & ZH20060_14, Iceland = EIPS2017H_1_workplace_2 & EIPS2017H_2_workplace_2, Netherlands = EIPS2017H_2_workplace, Norway = eips2017h_2_workplace, Sweden = EIPS2017H_2_workplace")
```

```{r}
kable(EIPS2017H_2_workplace, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden"))) 
```

#### EIPS2017H_1_media

>Media's position towards candidate 1

```{r}
kable(EIPS2017H_1_media_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C1_MEDIA, Germany = ZH29058_15 & ZH20060_15, Iceland = EIPS2017H_1_media_1 & EIPS2017H_2_media_1, Netherlands = EIPS2017H_1_media, Norway = eips2017h_1_media, Sweden = EIPS2017H_1_media")
```

```{r}
kable(EIPS2017H_1_media, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017H_2_media

>Media's position towards candidate 2

```{r}
kable(EIPS2017H_2_media_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C2_MEDIA, Germany = ZH29058_16 & ZH20060_16, Iceland = EIPS2017H_1_media_2 & EIPS2017H_2_media_2, Netherlands = EIPS2017H_2_media, Norway = eips2017h_2_media, Sweden = EIPS2017H_2_media")
```

```{r}
kable(EIPS2017H_2_media, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden"))) 
```

#### EIPS2017H_1_ideology

>Candidate 1's ideological placement on the left-right scale

```{r}
kable(EIPS2017H_1_ideology_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C1_IDEOLOGY, Germany = ZH29058_17 & ZH20060_17, Iceland = EIPS2017H_1_ideology_1 & EIPS2017H_2_ideology_1, Netherlands = EIPS2017H_1_ideology, Norway = eips2017h_1_ideology, Sweden = EIPS2017H_1_ideology")
```

```{r}
kable(EIPS2017H_1_ideology, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017H_2_ideology

>Candidate 2's ideological placement on the left-right scale

```{r}
kable(EIPS2017H_2_ideology_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))%>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C2_IDEOLOGY, Germany = ZH29058_18 & ZH20060_18, Iceland = EIPS2017H_1_ideology_2 & EIPS2017H_2_ideology_2, Netherlands = EIPS2017H_2_ideology, Norway = eips2017h_2_ideology, Sweden = EIPS2017H_2_ideology")
```

```{r}
kable(EIPS2017H_2_ideology, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden"))) 
```

#### EIPS2017H_1_immigration

>Candidate 1's attitude towards immigration

```{r}
kable(EIPS2017H_1_immigration_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C1_IMMIGRATION, Germany = ZH29058_19 & ZH20060_19, Iceland = EIPS2017H_1_immigration_1 & EIPS2017H_2_immigration_1, Netherlands = EIPS2017H_1_immigration, Norway = eips2017h_1_immigration, Sweden = EIPS2017H_1_immigration")
```

```{r}
kable(EIPS2017H_1_immigration, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden"))) 
```

#### EIPS2017H_2_immigration

>Candidate 2's attitude towards immigration

```{r}
kable(EIPS2017H_2_immigration_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names:** France = pe03_EIPS2017H_C2_IMMIGRATION, Germany = ZH29058_20 & ZH20060_20, Iceland = EIPS2017H_1_immigration_2 & EIPS2017H_2_immigration_2, Netherlands = EIPS2017H_2_immigration, Norway = eips2017h_2_immigration, Sweden = EIPS2017H_2_immigration")
```

```{r}
kable(EIPS2017H_2_immigration, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany ",	"Iceland", "Netherlands", "Norway", "Sweden"))) 
```

#### EIPS2017H_1_eumembership

> Candidate 1's attitude towards EU membership

```{r}
kable(EIPS2017H_1_eumembership_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = pe03_EIPS2017H_C1_EUMEMBERSHIP, Germany = ZH29058_21 & ZH20060_21, Iceland = EIPS2017H_1_eumembership_1 & EIPS2017H_2_eumembership_1, Netherlands = EIPS2017H_1_eumembership, Norway = eips2017h_1_eumembership, Sweden = EIPS2017H_1_eumembership")
```

```{r}
kable(EIPS2017H_1_eumembership, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```

#### EIPS2017H_2_eumembership

> Candidate 2's attitude towards EU membership

```{r}
kable(EIPS2017H_2_eumembership_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))%>%
  footnote(general = "Variable names : France = pe03_EIPS2017H_C2_EUMEMBERSHIP, Germany = ZH29058_22 & ZH20060_22, Iceland = EIPS2017H_1_eumembership_2 & EIPS2017H_2_eumembership_2, Netherlands = EIPS2017H_2_eumembership, Norway = eips2017h_2_eumembership, Sweden = EIPS2017H_2_eumembership")
```

```{r}
kable(EIPS2017H_2_eumembership, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany",	"Iceland", "Netherlands", "Norway", "Sweden")))
```

## EIPS2017I  

> Imagine that [EIPS2017I_community] has asked to rent a local community house in order to hold a meeting for its members and sympathizers. To what extent do you agree that the [EIPS2017I_community] should be allowed to rent the local community house for this purpose? 
Answer scale: [EIPS2017I]

This experiment  examines the legitimacy of the far right and the inclusion of Muslims into European societies. 

### EIPS2017I

```{r}
kable(EIPS2017I_q, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values", col.names = linebreak(c("EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names :France: pe03_EIPS2017I_COMMUNITY, Germany = expZH29062, Iceland = EIPS2017I_community, Netherlands = EIPS2017I_community, Norway = eips2017i_ran, Sweden = EIPS2017I_community")
```

```{r}
kable(EIPS2017I, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

### EIPS2017I_community

```{r}

kable(`EIPS2017I_community (RV)`, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden")))
```

## Rsp_Gender

> Gender distributions of the panel respondents.

```{r}
kable(`Gender`, booktabs = T, linesep = "", escape = F, caption = "Distributions", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) %>% 
  footnote(general = "Variable names : France = CAL_SEXE, Germany = gender_16, Iceland = kyn, Netherlands = geslacht, Norway = R9P1, Sweden = sex")
```

## Rsp_Age

> Age distributions of the panel respondents.

```{r}
kable(`Age`, booktabs = T, linesep = "", escape = F, caption = "Values and distributions", col.names = linebreak(c("Value", "N", "Age", "N", "Age", "N", "Age", "N", "Age", "N", "Age", "N"))) %>%
add_header_above(c("France" = 2, "Germany" = 2, "Iceland" = 2, "Netherlands" = 2, "Norway" = 2, "Sweden" = 2)) %>%
footnote(general = "Iceland, Netherlands, and Sweden have continuous age variables. In this table, they have been aggregated to 13 categories in line with the German variable. Variable names : France = CAL_AGE10, Germany = year_of_birth_cat_16, Iceland = aldur, Netherlands = gebjaar, Norway = R9P5_1, Sweden = age3")
```

## Rsp_Education

> Definitions of respondents' education levels vary between countries. Here, we provide a recommended harmonized categorization along with the original categories of each panel countries.

```{r}
kable(`Education`, booktabs = T, linesep = "", escape = F, caption = "Distributions, harmonized categories", col.names = linebreak(c("Value", "EIPS", "France", "Germany", "Iceland", "Netherlands", "Norway", "Sweden"))) 
```

### Education levels, France

>*Variable name:* CAL_DIPLOME  

Table: Original and recommended harmonized categories

| Value label | Origianl | Recommended category | Freq |
| :----: | ---------------------------- | -------- | ----: |
| **1** | Aucun/CEP/BEPC | Low | 340 |
| **2** | CAP/BEP | Medium | 554 |
| **3** | Bac/Bac+2 | High | 947 |
| **4** | Bac+3 et plus | High | 666 |



### Education levels, Germany

>*Variable name:* educ_job_16  

Table: Original and recommend harmonized categories 

| Value label | Original | Recommended | Freq |
| :----: | ---------------------------- | -------- | ----: |
| **1** | Noch in beruflicher Ausbildung (Berufsvorbereitungsjahr, Auszubildende/-r, Praktikant/-in, Student/-in) | Medium | 129 |
| **2** | Schüler/-in und besuche eine berufsorientierte Aufbau-, Fachschule o. ä. | Medium | 11 |
| **3** | Keinen beruflichen Abschluss und bin nicht in beruflicher Ausbildung | Low | 100 |
| **4** | Beruflich-betriebliche Berufsausbildung (Lehre) abgeschlossen | Medium | 963 |
| **5** | Beruflich-schulische Ausbildung (Berufsfachschule, Handelsschule, Vorbereitungsdienst für den mittleren Dienst in der öffentlichen Verwaltung) abgeschlossen | Medium | 235 |
| **6** | Ausbildung an einer Fachschule der DDR abgeschlossen | Medium | 63 |
| **7** | Ausbildung an einer Fach-, Meister-, Technikerschule, Berufs- oder Fachakademie abgeschlossen | Medium | 339 |
| **8** | Bachelor an (Fach-)Hochschule abgeschlossen | High | 85 |
| **9** | Fachhochschulabschluss (z. B. Diplom, Master) | High | 253 |
| **10** | Universitätsabschluss (z. B. Diplom, Magister, Staatsexamen, Master) | High | 388 |
| **11** | Promotion | High | 62 |
| **12** | Ein anderer beruflicher Abschluss, und zwar (bitte eintragen) | Other | 73 |
| **-90** | No answer | No answer | 1 |



### Education levels, Iceland

>*Variable name:* menntun  

Table: Original and recommended harmonized categories 

| Value label | Original | Recommended | Freq |
| :----: | ---------------------------- | -------- | ----: |
| **1** | Grunnskólanám eða minna | Low | 182 |
| **2** | Starfsnám | Medium | 120 |
| **3** | Iðnnám - verklegt nám á framhaldsskólastigi | Medium | 347 |
| **4** | Bóklegt nám á framhaldsskólastigi | Medium | 231 |
| **5** | Nám í sérskóla á háskólastigi | High | 119 |
| **6** | Grunnnám í háskóla | High | 484 |
| **7** | Meistaranám í háskóla | High | 349 |
| **8** | Doktorsnám | High | 29 |
| **9** | Annað, hvað | Other | 0 |
| **98** | Veit ekki | Other | 0 |
| **99** | Vil ekki svara | No Answer | 0 |


### Education levels, Netherlands

>*Variable name:* 

Table: Original and recommended harmonized categories 

| Value label | Original | Recommended | Freq |
| :----: | ---------------------------- | -------- | ----: |
| **1** | primary school | Low | 251 |
| **2** | vmbo (intermediate secondary education, US: junior high school) | Low | 1152 |
| **3** | havo/vwo (higher secondary education/preparatory university education, US: senior high school) | Medium | 632 |
| **4** | mbo (intermediate vocational education, US: junior college) | Medium | 1310 |
| **5** | hbo (higher vocational education, US: college) | High | 1405 |
| **6** | wo (university) | High | 653 |
| **7** | other | Other | 124 |
| **8** | Not (yet) completed any education | Low | 82 |
| **9** | Not yet started any education | Low | 13 |



### Education levels, Norway

>*Variable name:* R9P4_1  

Table: Original and recommended harmonized categories 

| Value label | Original | Recommended | Freq |
| :----: | ---------------------------- | -------- | ----: |
| **1** | Ingen utdanning/grunnskole | Low | 249 |
| **2** | Videregående skole | Medium | 815 |
| **3** | Høgskole/Universitet | High | 1572 |
| **97** | Ikke svart | Other | 70 |


### Education levels, Sweden

> *Variable name:* edu3  

Table: Original and recommended harmonized categories 

| Value label | Original | Recommended | Freq |
| :----: | ---------------------------- | -------- | ----: |
| **1** | Low edu | Low | 619 |
| **2** | Mid-lvl edu | Medium | 584 |
| **3** | High edu | High | 1223 |
| **.** | Missing | Missing | 81 |
