# Iceland

> Here follows some information about the ISSR, and the people involved in the project.

```{r ice_setup, include=FALSE, echo=FALSE}
if(!require("codebook")){install.packages("codebook");  library(codebook)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```
> Here follows some information about the SSRI, and the people involved in the project.


```{r ice_load_data}
di <- read_sav('C:\\Users/svein/Documents/nordforskdata/Terrorism_Iceland.sav') 
```
NOTES TO ICELAND:

- SOME TRANSLATIONS OF INTRODUCTION TEXTS ARE MISSING.
COULD YOU RETRIEVE THESE, IF POSSIBLE?

- For *NORDFORSK8_TREAT* AND *NORDFORSK8_DV*, THE ICELANDIC DATA SET HAS BEEN MODIFIED TO FIT THE STRUCTURE OF THE TABLES
AS A RESULT, THE NA VALUES OF *NORDFORSK8_DV* HAVE BEEN FILTERED OUT. 

- UNDER *NORDFORSK7*, THE ICELANDIC DATA SET HAS TWO MORE VARIABLES THAN THE OTHER DATA SETS DUE TO LANGUAGE DIFFERENCES (CONJUGATION OF SUBJECTS). 
I HAVE NOT INCLUDED *TERROR10_B* OR *TERROR10_C* IN THE GUIDE FOR THIS REASON, BUT PLEASE LET ME KNOW IF YOU OBJECT.

## Additional variables 

Below is an overview of the additional variables in the data set that have not yet been pooled. 
The project group will together determine which variables ought to be pooled across the three countries.

```{r ice_other}

other <- di %>% select(stada, atvinna, hjusk, fjoldi_heimili, fjoldi_barna, e_tekjur_lokad, h_tekjur_lokad)

codebook(other, detailed_variables = FALSE, detailed_scales = FALSE, missingness_report = FALSE)

```
