# Iceland

```{r ice_setup, include=FALSE, echo=FALSE}
if(!require("codebook")){install.packages("codebook");  library(codebook)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}

opts_chunk

```


```{r ice_load_data}
di <- read_sav('C:\\Users/svein/Documents/nordforskdata/Terrorism_Iceland.sav') 
```
NOTES TO ICELAND:

- SOME TRANSLATIONS OF INTRODUCTION TEXTS ARE MISSING: [NORDFORSK1]  [NORDFORSK7_EVENT], [NORDFORSK7_DV] 
COULD YOU RETRIEVE THESE, IF POSSIBLE?

- UNDER NORDFORSK7, THE ICELANDIC DATA SET HAS TWO MORE VARIABLES THAN THE OTHER DATA SETS DUE TO LANGUAGE DIFFERENCES (CONJUGATION OF SUBJECTS). 
I HAVE NOT INCLUDED TERROR10_B OR TERROR10_C IN THE GUIDE FOR THIS REASON, BUT PLEASE LET ME KNOW IF YOU OBJECT.

- For [NORDFORSK8_TREAT] AND [NORDFORSK8_DV], THE ICELANDIC DATA SET HAS BEEN MODIFIED TO FIT THE STRUCTURE OF THE TABLES
AS A RESULT, THE NA VALUES OF [NORDFORSK8_DV] HAVE BEEN FILTERED OUT. IF YOU HAVE THE OPPORTUNITY TO CHANGE THE ORIGINAL DATA SET 


