# Sweden

> Here follows some information about the Swedish Citizen Panel, and the people involved in the project.

```{r swe_setup, include=FALSE, echo=FALSE}
if(!require("codebook")){install.packages("codebook");  library(codebook)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```

```{r swe_load_data}

ds <- read_dta('C:\\Users/svein/Documents/nordforskdata/s5_sohlberg.dta') 

ds <- ds %>% select(-(starts_with('t_q')))
```

NOTES TO SWEDEN:

- FOR [NORDFORSK6_5] AND [NORDFORSK 6_6], THE VALUE 'EXTREMELY GOOD' IS MISSING FROM THE DATA, IT APPEARS. 
PLEASE CHECK AND CORRECT IF POSSIBLE.

- FOR [NORDFORSK8], THE VALUE 'IT LED TO A LOT LESS TERRORISM' IS MISSING FROM THE DATA, IT APPEARS. 
PLEASE CHECK AND CORRECT IF POSSIBLE.	

- FOR [NORDFORSK8_DV_1], THE VALUE 'DECREASE GREATLY' IS MISSING FROM THE DATA, IT APPEARS.

- FOR ALL RANDOMIZED EXPERIMENTAL VARIABLES THERE IS CONSISTENTLY AN EMPTY VALUE " " WHICH HAS A FREQUENCY OF 4. I HAVE DELETED THESE RESPONDENTS FROM THE DATA SET.

- SOME TRANSLATIONS OF INTRODUCTION TEXTS ARE MISSING: [NORDFORSK1] [NORDFORSK1_DV_B] [NORDFORSK6] [NORDFORSK7_EVENT], [NORDFORSK7_DV] 
COULD YOU RETRIEVE THESE, IF POSSIBLE?


## Additional variables 

Below is an overview of the additional variables in the data set that have not yet been pooled. 
(A set of time stamp variables are not displayed below, but available.)
The project group will together determine which variables ought to be pooled across the three countries.

```{r swe_other}

other <- ds %>% select(lrpown_mp36, edu_gammal, lrpown_gammal)

codebook(other, detailed_variables = FALSE, detailed_scales = FALSE, missingness_report = FALSE)

