# Final Words

```{r swe_setup, include=FALSE, echo=FALSE}
if(!require("codebook")){install.packages("codebook");  library(codebook)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}

```

```{r swe_load_data}

ds <- read_dta('C:\\Users/svein/Documents/nordforskdata/s5_sohlberg.dta') 

ds <- ds %>% select(-(starts_with('t_q')))
```

NOTES TO SWEDEN:

- FOR [NORDFORSK6_5] AND [NORDFORSK 6_6], THE VALUE 'EXTREMELY GOOD' IS MISSING FROM THE DATA. PLEASE CHECK AND CORRECT IF POSSIBLE.

- FOR ALL RANDOMIZED EXPERIMENTAL VARIABLES THERE IS CONSISTENTLY AN EMPTY VALUE " " WHICH HAS A FREQUENCY OF 4. I HAVE DELETED THESE RESPONDENTS FROM THE DATA SET.

- SOME TRANSLATIONS OF INTRODUCTION TEXTS ARE MISSING: [NORDFORSK1] [NORDFORSK6] [NORDFORSK7_EVENT], [NORDFORSK7_DV] 
COULD YOU RETRIEVE THESE, IF POSSIBLE?


