# Sweden

> Here follows some information about the Swedish Citizen Panel, and the people involved in the project.

```{r swe_setup, include=FALSE, echo=FALSE}
if(!require("codebook")){install.packages("codebook");  library(codebook)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```

```{r swe_load_data}

ds <- read_dta('C:\\Users/svein/Documents/nordforskdata/s5_sohlberg.dta') 

ds <- ds %>% select(-(starts_with('t_q')))
```

> Note on the Swedish data set:
For all randomized experimental variables, there is consistently an empty value " ", which has a frequency of 4. These are respondents who dropped out of the survey earlier, and have been deleted from the data set.


## Additional variables 

Below is an overview of the additional variables in the data set that have not yet been pooled. 
(A set of time stamp variables are not displayed below, but available.)
The project group will together determine which variables ought to be pooled across the three countries.

```{r swe_other}

other <- ds %>% select(lrpown_mp36, s5, edu_gammal, lrpown_gammal)

codebook(other, detailed_variables = FALSE, detailed_scales = FALSE, missingness_report = FALSE)
```
