# NORDFORSK1

```{r setup, include=FALSE, echo=FALSE}
if(!require("gt")){install.packages("gt");  library(gt)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("openxlsx")){install.packages("openxlsx");  library(openxlsx)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("sjlabelled")){install.packages("sjlabelled");  library(sjlabelled)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}
if(!require("webshot")){install.packages("webshot");  library(webshot)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```

This chapter displays tables with distributions for each variable included the conjoint experiment, labelled NORDFORSK 1, as well as question wordings and values for each individual panel.


>Could you please now imagine that an incident has taken place in the Nordic region and then consider some questions about the incident below.
The incident involves a [NORDFORSK1_TACTIC1] that targeted [NORDFORSK1_TARGET] [on Iceland / in Norway / in Sweden]. 
[NORDFORSK1_CASUALTIES] were killed in [NORDFORSK1_TACTIC2], which was performed by [NORDFORSK1_ADJECTIVE] [NORDFORSK1_SUBJECTIVE]. 
News coverage suggests [NORDFORSK1_MOTIVATION].

**Translations**
Icelandic
NA

Norwegian  
Vi ber deg nå se for deg en tenkt hendelse i Norden, og ta stilling til noen spørsmål vi stiller om hendelsen under.
Hendelsen gjelder en  [NORDFORSK1_TACTIC1] som fant sted [NORDFORSK1_TARGET] i Norge. 
[NORDFORSK1_CASUALTIES] ble drept i [NORDFORSK1_TACTIC2], som ble utført av [NORDFORSK1_ADJECTIVE] [NORDFORSK1_SUBJECTIVE].
Nyhetsdekningen tyder på [NORDFORSK1_MOTIVATION].

Swedish  
Vi ber dig nu att föreställa dig en påhittad händelse i Norden och svara på några frågor om
händelsen. 
[NORDFORSK1_TACTIC1] inträffade [NORDFORSK1_TARGET] i Sverige. [NORDFORSK1_CASUALTIES]
dödades i [NORDFORSK1_TACTIC2] som utfördes av [NORDFORSK1_ADJECTIVE]
[NORDFORSK1_SUBJECTIVE]. Nyhetsrapporteringen tyder på [NORDFORSK1_MOTIVATION].

## NORDFORSK1_TACTIC1
```{r conjoint_tactic1}

Source <- count(d_pool, NORDFORSK1_TACTIC1) %>% filter(n > 10)
#Source = c('protest', 'sabotage', 'hostage taking', 'shooting', 'bombing')
Iceland <- count(di_is, taktikk1)  
Norway <- count(dn, as_label(r15pad_terror1_ran1)) %>% filter(!is.na(`as_label(r15pad_terror1_ran1)`))
Sweden <- count(ds, q269_incidenttyp) %>% filter(n > 10)
tactic1 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(tactic1, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", 'n', "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = taktikk1, Norway =  r15pad_terror1_ran1, Sweden = q269_incidenttyp")
```

## NORDFORSK1_TARGET
```{r conjoint_target}
Source = c('a military facility', 'a police station', 'a school', 'a church', 'a mosque', 'a synagogue')
Iceland <- count(di_is, mal)  
Norway <- count(dn, as_label(r15pad_terror1_ran3)) %>% filter(!is.na(`as_label(r15pad_terror1_ran3)`))
Sweden <- count(ds, q269_plats) %>% filter(n > 10)
target <- bind_cols(Source, Iceland, Norway, Sweden)

kable(target, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = mal, Norway =  r15pad_terror1_ran3, Sweden = q269_plats")
```

## NORDFORSK1_CASUALTIES
```{r conjoint_casualties}                  
Source <-  c('No one', 'One person', 'Two people', 'Ten people')
Iceland <- count(di_is, personer)  
Norway <- count(dn, as_label(r15pad_terror1_ran4)) %>% filter(!is.na(`as_label(r15pad_terror1_ran4)`))
Sweden <- count(ds, q269_omkomna) %>% filter(n > 10)
casualties <- bind_cols(Source, Iceland, Norway, Sweden)

kable(casualties, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = personer, Norway =  r15pad_terror1_ran4, Sweden = q269_omkomna")
```

## NORDFORSK1_TACTIC2
```{r conjoint_tactic2}                
Source <- c('the protest', 'the sabotage', 'the hostage taking', 'the shooting', 'the bombing')
Iceland <- count(di_is, taktikk2)  
Norway <- count(dn, as_label(r15pad_terror1_ran5)) %>% filter(!is.na(`as_label(r15pad_terror1_ran5)`))
Sweden <- count(ds, q269_incidenten) %>% filter(n > 10)
tactic2 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(tactic2, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = taktikk2, Norway =  r15pad_terror1_ran5, Sweden = q269_incidenten")
```

## NORDFORSK1_ADJECTIVE
```{r conjoint_adjective}

Source = tibble(c('one', 'one Christian', 'one Muslim', 'one left-wing extremist', 'one right-wing extremist'))
Iceland <- count(di_is, adjektiv)  
Norway <- count(dn, as_label(r15pad_terror1_ran6)) %>% filter(!is.na(`as_label(r15pad_terror1_ran6)`))
Sweden <- count(ds, q269_ideologi) %>% filter(n > 10)
adjective <- bind_cols(Source, Iceland, Norway, Sweden)

kable(adjective, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = adjektiv, Norway =  r15pad_terror1_ran6, Sweden = q269_ideologi")
```                      
     
## NORDFORSK1_SUBJECTIVE                     
```{r conjoint_subject}                      
Source = c('organisation', 'group', 'individual', 'individual of unsound mind')
Iceland <- count(di_is, subjekt)  
Norway <- count(dn, as_label(r15pad_terror1_ran7)) %>% filter(!is.na(`as_label(r15pad_terror1_ran7)`))
Sweden <- count(ds, q269_subjekt) %>% filter(n > 10)
subject <- bind_cols(Source, Iceland, Norway, Sweden)

kable(subject, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = subjekt, Norway =  r15pad_terror1_ran7, Sweden = q269_subjekt")
```               

## NORDFORSK1_MOTIVATION
```{r conjoint_motivation}               
Source <- c('there was no clear motivation behind the incident', 'the incident was carried out with the aim of changing government policy', 'the motivation behind the incident came from a hatred towards the target')
Iceland <- count(di_is, motivasjon)  
Norway <- count(dn, as_label(r15pad_terror1_ran8)) %>% filter(!is.na(`as_label(r15pad_terror1_ran8)`))
Sweden <- count(ds, q269_motiv) %>% filter(n > 10)
motivation <- bind_cols(Source, Iceland, Norway, Sweden)

kable(motivation, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = motivasjon, Norway =  r15pad_terror1_ran8, Sweden = q269_motiv")

```
## NORDFORSK1_DV_A

> Would you classify this incident as an act of terrorism?

*Translations*

Iceland  
Myndir þú flokka þetta sem hryðjuverk?

Norway  
Vil du klassifisere denne hendelsen som terrorisme?

Sweden  
Skulle du säga att detta är terrorism?

```{r conjoint_dv_a}
Source <- c('Yes, this is terrorism', 'No, this is not terrorism', NA)
Iceland <- count(di_is, as_label(sp3))
Norway <- count(dn, as_label(r15pad_terror1_a)) %>% filter(`as_label(r15pad_terror1_a)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q270))
post <- bind_cols(Source, Iceland, Norway, Sweden)

kable(post, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = sp3, Norway =  r15pad_terror1_a, Sweden = q270")
```

## NORDFORSK1_DV_B

> Imagine that the authorities suspected that this incident was imminent. 
To what extent do you agree or disagree that the authorities should have the right to:

*Translations*

Iceland  
Ímyndum okkur að yfirvöld hefðu grun um að þetta atvik væri yfirvofandi. 
Hversu sammála eða ósammála ert þú því að yfirvöld ættu að hafa réttinn til að gera eftirfarandi?

Norway  
Tenk deg at myndighetene hadde mistanke om at denne hendelsen var nært forestående. Hvor enig eller uenig er du i at myndighetene burde har rett til å:

Sweden  
Föreställ dig att myndigheterna misstänkte att denna händelse var nära förestående. Hur
för eller emot är du att myndigheterna borde ha rätt till att:


### NORDFORSK1_DV_B_1

> Hold people in custody as long as they want without charging them

*Translations*

Icelandic  
Halda fólki í gæsluvarðhaldi eins lengi og þau vilja án ákæru.

Norway  
Holde personer i forvaring så lenge de vil uten å stille dem for retten.

Sweden  
Hålla personer häktade utan att ställa inför rätta.


```{r conjoint_dv_b_1}

Source <- c('Strongly agree', 'Agree', 'Agree somewhat', 'Neither agree nor disagree', 'Disagree somewhat', 'Disagree', 'Strongly disagree', NA)
Iceland <- count(di_is, as_label(sp4_1))
Norway <- count(dn, as_label(r15pad_terror1_b_1)) %>% filter(`as_label(r15pad_terror1_b_1)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q272_1))
post <- bind_cols(Source, Iceland, Norway, Sweden)

kable(post, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = sp4_1, Norway =  r15pad_terror1_b_1, Sweden = q272_1")
```

### NORDFORSK1_DV_B_2

> Listen in on people's telephone conversations

*Translations*

Icelandic  
Hlera símtöl fólks

Norway  
Avlytte folks telefonsamtaler

Sweden  
Avlyssna människors telefonsamtal


```{r conjoint_dv2_b_2}

Source <- c('Strongly agree', 'Agree', 'Agree somewhat', 'Neither agree nor disagree', 'Disagree somewhat', 'Disagree', 'Strongly disagree', NA)
Iceland <- count(di_is, as_label(sp4_2))
Norway <- count(dn, as_label(r15pad_terror1_b_2)) %>% filter(`as_label(r15pad_terror1_b_2)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q272_2))
post <- bind_cols(Source, Iceland, Norway, Sweden)

kable(post, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = sp4_2, Norway =  r15pad_terror1_b_2, Sweden = q272_2")
```

### NORDFORSK1_DV_B_3

> Randomly stop and search people on the street

*Translations*

Icelandic  
Stöðva fólk af handahófi úti á götu og leita á því

Norway  
Tilfeldig stoppe og ransake folk på gaten

Sweden  
Tillfälligt stoppa och visitera människor på gatan


```{r conjoint_dv2_b_3}

Source <- c('Strongly agree', 'Agree', 'Agree somewhat', 'Neither agree nor disagree', 'Disagree somewhat', 'Disagree', 'Strongly disagree', NA)
Iceland <- count(di_is, as_label(sp4_3))
Norway <- count(dn, as_label(r15pad_terror1_b_3)) %>% filter(`as_label(r15pad_terror1_b_3)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q272_3))
post <- bind_cols(Source, Iceland, Norway, Sweden)

kable(post, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = sp4_3, Norway =  r15pad_terror1_b_3, Sweden = q272_3")
```

### NORDFORSK1_DV_B_4

> Conduct surveillance of people's Email and Internet communications

*Translations*

Icelandic  
Fylgjast með tölvupósti fólks og öðrum upplýsingum sem sendar eru á netinu

Norway  
Overvåke folks epost og internettkommunikasjon

Sweden  
Övervaka människors epost och internetkommunikation


```{r conjoint_dv2_b_4}

Source <- c('Strongly agree', 'Agree', 'Agree somewhat', 'Neither agree nor disagree', 'Disagree somewhat', 'Disagree', 'Strongly disagree', NA)
Iceland <- count(di_is, as_label(sp4_4))
Norway <- count(dn, as_label(r15pad_terror1_b_4)) %>% filter(`as_label(r15pad_terror1_b_4)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q272_4))
post <- bind_cols(Source, Iceland, Norway, Sweden)

kable(post, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = sp4_4, Norway =  r15pad_terror1_b_4, Sweden = q272_4")
```

### NORDFORSK1_DV_B_5

> Conduct surveillance/wire tapping of rooms

*Translations*

Icelandic  
Vakta/hlera húsnæði fólks

Norway  
Overvåke/avlytte rom

Sweden  
Övervaka/avlyssna rum

```{r conjoint_dv2_b_5}

Source <- c('Strongly agree', 'Agree', 'Agree somewhat', 'Neither agree nor disagree', 'Disagree somewhat', 'Disagree', 'Strongly disagree', NA)
Iceland <- count(di_is, as_label(sp4_5))
Norway <- count(dn, as_label(r15pad_terror1_b_5)) %>% filter(`as_label(r15pad_terror1_b_5)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q272_5))
post <- bind_cols(Source, Iceland, Norway, Sweden)

kable(post, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = sp4_5, Norway =  r15pad_terror1_b_5, Sweden = q272_5")
```

### NORDFORSK1_DV_B_6

> Cordon off parts of the city

*Translations*

Icelandic  
Loka af hluta borgarinnar/bæjarins

Norway  
Sperre av deler av byrommet

Sweden  
Spärra av delar av staden/orten


```{r conjoint_dv2_b_6}

Source <- c('Strongly agree', 'Agree', 'Agree somewhat', 'Neither agree nor disagree', 'Disagree somewhat', 'Disagree', 'Strongly disagree', NA)
Iceland <- count(di_is, as_label(sp4_6))
Norway <- count(dn, as_label(r15pad_terror1_b_6)) %>% filter(`as_label(r15pad_terror1_b_6)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q272_6))
post <- bind_cols(Source, Iceland, Norway, Sweden)

kable(post, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = sp4_6, Norway =  r15pad_terror1_b_6, Sweden = q272_6")
```

### NORDFORSK1_DV_B_7

> Let armed police or the army patrol the streets

*Translations*

Icelandic  
Láta vopnaða lögreglu eða her vakta göturnar

Norway  
La bevæpnet politi eller forsvaret patruljere gatene

Sweden  
Låta beväpnad polis eller försvaret patrullera gatorn

```{r conjoint_dv2_b_7}

Source <- c('Strongly agree', 'Agree', 'Agree somewhat', 'Neither agree nor disagree', 'Disagree somewhat', 'Disagree', 'Strongly disagree', NA)
Iceland <- count(di_is, as_label(sp4_7))
Norway <- count(dn, as_label(r15pad_terror1_b_7)) %>% filter(`as_label(r15pad_terror1_b_7)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q272_7))
post <- bind_cols(Source, Iceland, Norway, Sweden)

kable(post, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = sp4_7, Norway =  r15pad_terror1_b_7, Sweden = q272_7")
```

