---
output:
  word_document: default
  html_document: default
---
# EIPS variables: Formulations and distributions {#variables}

```{r setup, include=FALSE, echo=FALSE}
if(!require("gt")){install.packages("gt");  library(gt)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("openxlsx")){install.packages("openxlsx");  library(openxlsx)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("sjlabelled")){install.packages("sjlabelled");  library(sjlabelled)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}
if(!require("webshot")){install.packages("webshot");  library(webshot)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```


This chapter displays tables with distributions for each variable included in the survey, as well as question wordings and values for each individual panel.

## NORDFORSK1

>Could you please now imagine that an incident has taken place in the Nordic region and then consider some questions about the incident below.
The incident involves a [Tactic 1] that targeted [Target] [on Iceland / in Norway / in Sweden]. 
[Casualties] were killed in [Tactic 2], which was performed by [Adjective] [Subjective]. 
News coverage suggests [Motivation].

**Translations**
Icelandic

Norwegian  
Vi ber deg nå se for deg en tenkt hendelse i Norden, og ta stilling til noen spørsmål vi stiller om hendelsen under.
Hendelsen gjelder en  [Tactic 1] som fant sted [Target] i Norge. 
[Casualties] ble drept i [Tactic2], som ble utført av [Adjective] [Subjective].
Nyhetsdekningen tyder på [Motivation].

Swedish  

### NORDFORSK1_TACTIC1
```{r conjoint_tactic1}
Source = c('protest', 'sabotage', 'hostage taking', 'shooting', 'bombing')
Iceland <- count(di, taktikk1)  
Norway <- count(dn, as_label(r15pad_terror1_ran1)) %>% filter(!is.na(`as_label(r15pad_terror1_ran1)`))
Sweden <- count(ds, q269_incidenttyp) %>% filter(n > 10)
tactic1 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(tactic1, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = taktikk1, Norway =  r15pad_terror1_ran1, Sweden = q269_incidenttyp")
```

### NORDFORSK1_TARGET
```{r conjoint_target}
Source = c('a military facility', 'a police station', 'a school', 'a church', 'a mosque', 'a synagogue')
Iceland <- count(di, mal)  
Norway <- count(dn, as_label(r15pad_terror1_ran3)) %>% filter(!is.na(`as_label(r15pad_terror1_ran3)`))
Sweden <- count(ds, q269_plats) %>% filter(n > 10)
target <- bind_cols(Source, Iceland, Norway, Sweden)

kable(target, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = mal, Norway =  r15pad_terror1_ran3, Sweden = q269_plats")
```

### NORDFORSK1_CASUALTIES
```{r conjoint_casualties}                  
Source <-  c('No one', 'One person', 'Two people', 'Ten people')
Iceland <- count(di, personer)  
Norway <- count(dn, as_label(r15pad_terror1_ran4)) %>% filter(!is.na(`as_label(r15pad_terror1_ran4)`))
Sweden <- count(ds, q269_omkomna) %>% filter(n > 10)
casualties <- bind_cols(Source, Iceland, Norway, Sweden)

kable(casualties, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = personer, Norway =  r15pad_terror1_ran4, Sweden = q269_omkomna")
```

### NORDFORSK1_TACTIC2
```{r conjoint_tactic2}                
Source <- c('the protest', 'the sabotage', 'the hostage taking', 'the shooting', 'the bombing')
Iceland <- count(di, taktikk2)  
Norway <- count(dn, as_label(r15pad_terror1_ran5)) %>% filter(!is.na(`as_label(r15pad_terror1_ran5)`))
Sweden <- count(ds, q269_incidenten) %>% filter(n > 10)
tactic2 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(tactic2, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = taktikk2, Norway =  r15pad_terror1_ran5, Sweden = q269_incidenten")
```

### NORDFORSK1_ADJECTIVE
```{r conjoint_adjective}

Source = tibble(c('one', 'one Christian', 'one Muslim', 'one left-wing extremist', 'one right-wing extremist'))
Iceland <- count(di, adjektiv)  
Norway <- count(dn, as_label(r15pad_terror1_ran6)) %>% filter(!is.na(`as_label(r15pad_terror1_ran6)`))
Sweden <- count(ds, q269_ideologi) %>% filter(n > 10)
adjective <- bind_cols(Source, Iceland, Norway, Sweden)

kable(adjective, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = adjektiv, Norway =  r15pad_terror1_ran6, Sweden = q269_ideologi")

#adjective <- left_join(adjective_src, adjective_ice, adjective_no, adjective_swe)

``````                      
     
### NORDFORSK1_MOTIVATION                      
```{r conjoint_subject}                      
Source = c('organisation', 'group', 'individual', 'individual of unsound mind')
Iceland <- count(di, subjekt)  
Norway <- count(dn, as_label(r15pad_terror1_ran7)) %>% filter(!is.na(`as_label(r15pad_terror1_ran7)`))
Sweden <- count(ds, q269_subjekt) %>% filter(n > 10)
subject <- bind_cols(Source, Iceland, Norway, Sweden)

kable(subject, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = subjekt, Norway =  r15pad_terror1_ran7, Sweden = q269_subjekt")
```               

### NORDFORSK1_MOTIVATION
```{r conjoint_motivation}               
Source <- c('there was no clear motivation behind the incident', 'the incident was carried out with the aim of changing government policy', 'the motivation behind the incident came from a hatred towards the target')
Iceland <- count(di, motivasjon)  
Norway <- count(dn, as_label(r15pad_terror1_ran8)) %>% filter(!is.na(`as_label(r15pad_terror1_ran8)`))
Sweden <- count(ds, q269_motiv) %>% filter(n > 10)
motivation <- bind_cols(Source, Iceland, Norway, Sweden)

kable(motivation, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
 footnote(general = "Variable names. Iceland = motivasjon, Norway =  r15pad_terror1_ran8, Sweden = q269_motiv")

```
### NORDFORSK1_DV


