# NORDFORSK2

```{r setup, include=FALSE, echo=FALSE}
if(!require("gt")){install.packages("gt");  library(gt)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("openxlsx")){install.packages("openxlsx");  library(openxlsx)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("sjlabelled")){install.packages("sjlabelled");  library(sjlabelled)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}
if(!require("webshot")){install.packages("webshot");  library(webshot)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```


This chapter displays tables with distributions for each variable included the, labelled NORDFORSK 1, as well as question wordings and values for each individual panel.

## NORDFORSK2

>Could you please now imagine that an incident has taken place in the Nordic region and then consider some questions about the incident below.
The incident involves a [Tactic 1] that targeted [Target] [on Iceland / in Norway / in Sweden]. 
[Casualties] were killed in [Tactic 2], which was performed by [Adjective] [Subjective]. 
News coverage suggests [Motivation].

**Translations**
Icelandic

Norwegian  
Vi ber deg nå se for deg en tenkt hendelse i Norden, og ta stilling til noen spørsmål vi stiller om hendelsen under.
Hendelsen gjelder en  [Tactic 1] som fant sted [Target] i Norge. 
[Casualties] ble drept i [Tactic2], som ble utført av [Adjective] [Subjective].
Nyhetsdekningen tyder på [Motivation].

Swedish  

### NORDFORSK2_A

```{r conjoint_tactic1}
Source = c('protest', 'sabotage', 'hostage taking', 'shooting', 'bombing')
Iceland <- count(di, taktikk1)  
Norway <- count(dn, as_label(r15pad_terror1_ran1)) %>% filter(!is.na(`as_label(r15pad_terror1_ran1)`))
Sweden <- count(ds, q269_incidenttyp) %>% filter(n > 10)
tactic1 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(tactic1, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = taktikk1, Norway =  r15pad_terror1_ran1, Sweden = q269_incidenttyp")
```
