# NORDFORSK3

```{r nordforsk3_setup, include=FALSE, echo=FALSE}
if(!require("gt")){install.packages("gt");  library(gt)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("openxlsx")){install.packages("openxlsx");  library(openxlsx)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("sjlabelled")){install.packages("sjlabelled");  library(sjlabelled)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}
if(!require("webshot")){install.packages("webshot");  library(webshot)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```

> To what extent do you agree that the safeguarding of society's security should be at the expense of individuals' freedom (such
as protection of privacy and the right to privacy)?

*Translations*

Icelandic  
Hversu sammála ert þú að verndun öryggis í samfélaginu ætti að vera á kostnað einstaklingsfrelsis (til dæmis persónuverndar og réttinum til einkalífs)?

Norway  
Ivaretakelse av sikkerhet bør gå på bekostning av enkeltindividers frihet.

Sweden  
I vilken utsträckning samhällets säkerhet på bekostnad av individers frihet?

```{r nordforsk3}
Source = c('Strongly agree', 'Agree', 'Agree somewhat', 'Neither agree nor disagree', 'Disagree somewhat', 'Disagree', 'Strongly disagree', NA)
Iceland <- count(di, as_label(sp6))  
Norway <- count(dn, as_label(r15pad_terror3)) %>% filter(`as_label(r15pad_terror3)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q276)) %>% filter(n > 10)
nordforsk3 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(nordforsk3, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp6, Norway =  r15pad_terror3, Sweden = q276")
```
