# NORDFORSK6

```{r nordforsk6_setup, include=FALSE, echo=FALSE}
if(!require("gt")){install.packages("gt");  library(gt)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("openxlsx")){install.packages("openxlsx");  library(openxlsx)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("sjlabelled")){install.packages("sjlabelled");  library(sjlabelled)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}
if(!require("webshot")){install.packages("webshot");  library(webshot)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```

> In your opinion, how good or bad are the following actors [on Iceland / in Norway / in Sweden] regarding their ability to deal with the risk of terrorist attacks?

*Translations*

Iceland  
Hversu vel eða illa telur þú að eftirfarandi aðilar á Íslandi séu í stakk búnir til að bregðast við hættunni sem stafar af hryðjuverkaárásum? 

Norway  
Hvor godt i stand til å håndtere terrorangrep: 

Sweden 
Hantera risk terrorattacker: 

## NORDFORSK6_1

> International organizations

Iceland  
Alþjóðastofnanir

Norway  
Internasjonale organisasjoner

Sweden  
Internationella organisationer

```{r nordforsk6_1}
Source <- c('Extremely good', 'Very good', 'Somewhat good', 'Neither good nor bad', 'Somewhat bad', 'Very bad', 'Extremely bad', NA)
Iceland <- count(di, as_label(sp9_1))
Norway <- count(dn, as_label(r15pad_terror8_1)) %>% filter(`as_label(r15pad_terror8_1)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q282_1))
nordforsk6_1 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(nordforsk6_1, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp9_1, Norway =  r15pad_terror8_1, Sweden = q282_1")
```

## NORDFORSK6_2

> National authorities

Iceland  
Ríkisstjórnin

Norway  
Nasjonale myndigheter

Sweden  
Nationella myndigheter

```{r nordforsk6_2}
Source <- c('Extremely good', 'Very good', 'Somewhat good', 'Neither good nor bad', 'Somewhat bad', 'Very bad', 'Extremely bad', NA)
Iceland <- count(di, as_label(sp9_2)) 
Norway <- count(dn, as_label(r15pad_terror8_2)) %>% filter(`as_label(r15pad_terror8_2)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q282_2))
nordforsk6_2 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(nordforsk6_2, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp9_2, Norway =  r15pad_terror8_2, Sweden = q282_2")
```

## NORDFORSK6_3

> Local authorities

Iceland  
Sveitarstjórnir

Norway  
Lokale myndigheter

Sweden  
Lokala myndigheter

```{r nordforsk6_3}
Source <- c('Extremely good', 'Very good', 'Somewhat good', 'Neither good nor bad', 'Somewhat bad', 'Very bad', 'Extremely bad', NA)
Iceland <- count(di, as_label(sp9_3)) 
Norway <- count(dn, as_label(r15pad_terror8_3)) %>% filter(`as_label(r15pad_terror8_3)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q282_3))
nordforsk6_3 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(nordforsk6_3, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp9_3, Norway =  r15pad_terror8_3, Sweden = q282_3")
```

## NORDFORSK6_4

> The police

Iceland  
Lögreglan

Norway  
Politiet

Sweden  
Polisen   

```{r nordforsk6_4}
Source <- c('Extremely good', 'Very good', 'Somewhat good', 'Neither good nor bad', 'Somewhat bad', 'Very bad', 'Extremely bad', NA)
Iceland <- count(di, as_label(sp9_4)) 
Norway <- count(dn, as_label(r15pad_terror8_4)) %>% filter(`as_label(r15pad_terror8_4)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q282_4))
nordforsk6_4 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(nordforsk6_4, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp9_4, Norway =  r15pad_terror8_4, Sweden = q282_4")
```

## NORDFORSK6_5

> NGOs

Iceland  
Frjáls félagasamtök

Norway  
Frivillige organisasjoner

Sweden  
Frivilligorganisationer

```{r nordforsk6_5}
Source <- c('Extremely good', 'Very good', 'Somewhat good', 'Neither good nor bad', 'Somewhat bad', 'Very bad', 'Extremely bad', NA)
Iceland <- count(di, as_label(sp9_5)) 
Norway <- count(dn, as_label(r15pad_terror8_5)) %>% filter(`as_label(r15pad_terror8_5)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q282_5)) %>% add_row(`as_label(q282_5)`=NA, n= NA, .before=1)
nordforsk6_5 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(nordforsk6_5, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp9_5, Norway =  r15pad_terror8_5, Sweden = q282_5") %>% 
  footnote(general = 'Obs! Value *Extremt bra* appears to be missing in the data set')
```

## NORDFORSK6_6

> Individual citizens

Iceland  
Almennir borgarar

Norway  
Den enkelte innbygger

Sweden  
Den enskilde invånaren

```{r nordforsk6_6}
Source <- c('Extremely good', 'Very good', 'Somewhat good', 'Neither good nor bad', 'Somewhat bad', 'Very bad', 'Extremely bad', NA)
Iceland <- count(di, as_label(sp9_6)) 
Norway <- count(dn, as_label(r15pad_terror8_6)) %>% filter(`as_label(r15pad_terror8_6)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q282_6)) %>% add_row(`as_label(q282_6)`=NA, n=NA, .before = 1)
nordforsk6_6 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(nordforsk6_6, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp9_6, Norway =  r15pad_terror8_6, Sweden = q282_6") %>% 
  footnote(general = 'Obs! Value *Extremt bra* appears to be missing in the data set')
```
