# NORDFORSK8

```{r NORDFORSK7_setup, include=FALSE, echo=FALSE}
if(!require("gt")){install.packages("gt");  library(gt)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("openxlsx")){install.packages("openxlsx");  library(openxlsx)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("sjlabelled")){install.packages("sjlabelled");  library(sjlabelled)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}
if(!require("webshot")){install.packages("webshot");  library(webshot)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```


> Over the past twenty years, there have been high levels of immigration from Muslim countries in Africa, Asia and the Middle
East to Europe.
There are differences in how strict certain countries are regarding their immigration policies. There are also differences
regarding which countries Muslims typically prefer to emigrate to. By gathering large amounts of data, researchers can use
these differences to study the correlation between Muslim immigration and terrorism.
A US research team recently used data from 174 countries during the period of 1995-2015 to study how the probability of
terrorism changed as a result of increased immigration from Muslim countries.


*Translations*

Iceland  
NA 

Norway  
I løpet av de siste tjue årene har det vært høy innvandring fra muslimske land i Afrika, Asia og Midtøsten til Europa.
Det er variasjon i hvor streng innvandringspolitikk som praktiseres mellom land. Det er også variasjon med tanke på hvilke
land muslimer typisk foretrekker å emigrere til. Ved å samle store mengder data kan forskere bruke denne variasjonen til å
studere sammenhengen mellom muslimsk innvandring og terrorisme.
Et forskerteam fra USA brukte nylig data fra 174 land i perioden 1995-2015 til å studere hvordan sannsynligheten for
terrorisme endret seg som følge av økt innvandring fra muslimske land.

Sweden 
NA


## NORDFORSK7

>  During the period of 1995-2015, how do you think increased immigration from Muslim-majority countries influenced
recipient countries?


*Translations*

Iceland
Hvaða áhrif telur þú að aukinn fjöldi innflytjenda frá löndum þar sem múslimar eru í meirihluta hafi haft á móttökulöndin á árunum 1995 til 2015?

Norway  
I løpet av perioden 1995-2015, hvordan tror du økt innvandring fra muslimske majoritetsland påvirket mottakerlandene?

Sweden  
NA

```{r NORDFORSK8}
Source <- c('It led to a lot more terrorism', 'It led to somewhat more terrorism', 'It did not lead to any more or any less terrorism', 'It led to less terrorism', 'It led to a lot less terrorism', NA)
Iceland <- count(di, as_label(sp12))
Norway <- count(dn, as_label(r15pad_terror11pre)) %>% filter(`as_label(r15pad_terror11pre)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q286)) %>% add_row(`as_label(q286)` = NA, n=NA, .before = 5)
NORDFORSK8 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(NORDFORSK8, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Source Questionnaire", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp12, Norway =  r15pad_terror11pre, Sweden = q286")
```
