# NORDFORSK8

```{r NORDFORSK8_setup, include=FALSE, echo=FALSE}
if(!require("gt")){install.packages("gt");  library(gt)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("openxlsx")){install.packages("openxlsx");  library(openxlsx)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("sjlabelled")){install.packages("sjlabelled");  library(sjlabelled)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}
if(!require("webshot")){install.packages("webshot");  library(webshot)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```


> Over the past twenty years, there have been high levels of immigration from Muslim countries in Africa, Asia and the Middle
East to Europe.
There are differences in how strict certain countries are regarding their immigration policies. There are also differences
regarding which countries Muslims typically prefer to emigrate to. By gathering large amounts of data, researchers can use
these differences to study the correlation between Muslim immigration and terrorism.
A US research team recently used data from 174 countries during the period of 1995-2015 to study how the probability of
terrorism changed as a result of increased immigration from Muslim countries.


*Translations*

Iceland  
Til upplýsingar, rannsakendurnir sem greindu tengslin milli innflytjenda frá löndum þar sem múslimar eru í meirihluta og hryðjuverkaárása í móttökulöndum komust að því að aukinn fjöldi innflytjenda frá múslimskum löndum hefði engin áhrif á fjölda hryðjuverka í móttökulöndunum.Telur þú að 

Norway  
I løpet av de siste tjue årene har det vært høy innvandring fra muslimske land i Afrika, Asia og Midtøsten til Europa.
Det er variasjon i hvor streng innvandringspolitikk som praktiseres mellom land. Det er også variasjon med tanke på hvilke
land muslimer typisk foretrekker å emigrere til. Ved å samle store mengder data kan forskere bruke denne variasjonen til å
studere sammenhengen mellom muslimsk innvandring og terrorisme.
Et forskerteam fra USA brukte nylig data fra 174 land i perioden 1995-2015 til å studere hvordan sannsynligheten for
terrorisme endret seg som følge av økt innvandring fra muslimske land.

Sweden  
Under de senaste tjugo åren har det varit hög invandring från muslimska länder i Afrika,
Asien och Mellanöstern till Europa.
Det finns skillnader i hur strikt invandringspolitik olika länder har.
Det finns också skillnader gällande vilka länder muslimer vanligtvis föredrar att emigrera till.
Genom att samla in stora mängder data kan forskare använda dessa skillnader till att studera förhållandet mellan muslimsk invandring och terrorism.
Ett amerikanskt forskarteam använde nyligen data från 174 länder under perioden 1995-2015 för att studera hur sannolikheten för terrorism förändrades till följd av ökad invandring från muslimska länder.


## NORDFORSK8_PRE

>  During the period of 1995-2015, how do you think increased immigration from Muslim-majority countries influenced
recipient countries?


*Translations*

Iceland
Hvaða áhrif telur þú að aukinn fjöldi innflytjenda frá löndum þar sem múslimar eru í meirihluta hafi haft á móttökulöndin á árunum 1995 til 2015?

Norway  
I løpet av perioden 1995-2015, hvordan tror du økt innvandring fra muslimske majoritetsland påvirket mottakerlandene?

Sweden  
Under perioden 1995-2015, hur tror du att ökad invandring från muslimska majoritetsländer har
påverkat mottagarländerna?

```{r NORDFORSK8_PRE}
Source <- c('It led to a lot more terrorism', 'It led to somewhat more terrorism', 'It did not lead to any more or any less terrorism', 'It led to less terrorism', 'It led to a lot less terrorism', NA)
Iceland <- count(di_is, as_label(sp12))
Norway <- count(dn, as_label(r15pad_terror11pre)) %>% filter(`as_label(r15pad_terror11pre)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q286)) %>% add_row(`as_label(q286)` = NA, n=NA, .before = 5)
NORDFORSK8 <- bind_cols(Source, Iceland, Norway, Sweden)

kable(NORDFORSK8, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp12, Norway =  r15pad_terror11pre, Sweden = q286") %>% 
  footnote(general = "Value *Det ledde till mindre terrorism* appears to be missing in the data set. The reason is that no answer was recorded for this value. The respondents did have that response option available when answering the survey.")
```

## NORDFORSK8_TREAT

Note that the Iceland responses were split into two variables, where sp13 refers to the variable name of the treatment group and sp14 refers to the control group.
The original sp13 and sp14 Icelandic data set has been pivoted long 'nordforsk8_treat' lists the random assignment to treatment groups and 'nordforsk8_dv' refers to the respondents' responses:
```{r NORDFORSK8_pivot}
#ddi <- di %>% mutate(temp = case_when(is.na(sp13)) ~ 99) 
ddi <- pivot_longer(di_is, sp13:sp14, names_to = 'ice_nordforsk8_treat', values_to = 'ice_nordforsk8_dv', values_drop_na = TRUE)
```

```{r NORDFORSK8_TREAT}

Source <- c('For your information, the researchers who analysed the correlation between immigration from Muslim countries and terrorist attacks in recipient countries, found that increased Muslim immigration had no impact on terrorism in recipient countries.', " ")
Iceland <- count(ddi, as_label(ice_nordforsk8_treat))
Norway <- count(dn, as_label(r15pad_terror11_ran)) %>% filter(!is.na(`as_label(r15pad_terror11_ran)`))
ds <- ds  %>% set_labels(q288, labels = c('För din kännedom, forskarna som analyserade sambandet mellan invandring från muslimska länder och terroristattacker i värdländerna fann ingen påverkan från ökad muslimsk invandring på terrorism i mottagarländerna.' = 1,
                                        ' ' = 0))
Sweden <- count(ds, as_label(q288)) %>% filter(n>10)
NORDFORSK8_TREAT <- bind_cols(Source, Iceland, Norway, Sweden)

kable(NORDFORSK8_TREAT, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp13 and sp14, Norway =  r15pad_terror11_ran, Sweden = q286. Note that the Iceland responses were split into two variables, where sp13 refers to the variable name of the treatment group and sp14 refers to the control group.")

```

## NORDFORSK8_DV_A
 > Over the next ten years, do you think the terror threat in [country] will increase if we choose to receive more immigrants from Muslim countries in Africa, Asia, and the Middle East? The terror threat will...

*Transalations*

Iceland  

Telur þú að hryðjuverkaógnin á Íslandi muni aukast á næstu tíu árum ef við tökum á móti fleiri innflytjendum frá múslimskum löndum í Afríku, Asíu og Miðausturlöndum?

Norway  
I løpet av de neste ti årene, tror du terrorfaren i Norge vil øke hvis vi velger å ta imot flere innvandrere fra muslimske land i Afrika, Asia og Midtøsten? Terrorfaren vil...

Sweden  
Inom de kommande tio åren, tror du att risken för terrorattacker i Sverige kommer att öka om vi väljer att ta emot fler invandrare från muslimska länder i Afrika, Asien och Mellanöstern? Risken för terrorattacker kommer att…

```{r NORDFORSK8_DV_A}

# Source <- c('Increase greatly', 'Increase', 'Increase somewhat', 'Neither increase nor decrease', 'Decrease somewhat', 'Decrease', 'Decrease greatly', NA)
# Iceland <- count(ddi_is, as_label(ice_nordforsk8_dv)) %>% add_row(`as_label(ice_nordforsk8_dv)`= NA, n = NA)
# Norway <- count(dn, as_label(r15pad_terror11posta)) %>% filter(`as_label(r15pad_terror11posta)` != 'Ikke spurt')
# Sweden <- count(ds, as_label(q290)) %>% add_row(`as_label(q290)` = NA, n = NA, .before = 7)
# NORDFORSK8_DV_A <- bind_cols(Source, Iceland, Norway, Sweden)
# 
# kable(NORDFORSK8_DV_A, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
#   footnote(general = "Variable names. Iceland = sp13 and sp14, Norway =  r15pad_terror11posta, Sweden = q290. Note that the Iceland responses were split into two variables, where sp13 refers to the variable name of the treatment group and sp14 refers to the control group.") %>% 
#   footnote(general = "Value *Minska kraftigt* appears to be missing in the data set. The reason is that no answer was recorded for this value. The respondents did have that response option available when answering the survey.")

```


## NORDFORSK8_DV_B

>There is an ongoing debate in Norway about how many refugees we should receive. 
Do you think Norway should receive more or fewer refugees than it does today?

*Transalations*

Iceland  
Nú stendur yfir umræða á Íslandi um hversu mörgum flóttamönnum við eigum að taka á móti. Telur þú að Ísland eigi að taka á móti fleiri eða færri flóttamönnum en gert er í dag?

Norway  
Det er en pågående debatt i Norge om hvor mange flyktninger vi bør ta imot. Synes du Norge bør ta imot flere eller færre flyktninger enn i dag?

Sweden  
Tycker du att Sverige bör ta emot fler eller färre flyktingar än idag? 

```{r NORDFORSK8_DV_B}

Source <- c('Receive many more', 'Receive more', 'Receive a few more', 'Neither receive any more nor any less', 'Receive a few less', 'Receive fewer', 'Receive many fewer', NA)
Iceland <- count(di_is, as_label(sp15))
Norway <- count(dn, as_label(r15pad_terror11postb)) %>% filter(`as_label(r15pad_terror11postb)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q292)) 
NORDFORSK8_DV_B <- bind_cols(Source, Iceland, Norway, Sweden)

kable(NORDFORSK8_DV_B, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp15, Norway =  r15pad_terror11postb, Sweden = q292.")
```

## NORDFORSK8_DV_C

> To what extent do you agree or disagree that Norway should reduce the proportion of refugees with Muslim backgrounds?

*Transalations*

Iceland  

Hversu sammála eða ósammála ert þú að Ísland eigi að reyna að lækka hlutfall flóttamanna sem eru múslimar?

Norway  
Noen mener Norge bør redusere andelen muslimske flyktninger vi tar imot.
Hvor enig eller uenig er du i at Norge bør redusere andelen flyktninger med muslimsk bakgrunn?

Sweden  
Hur för eller emot Sverige  minska andelen flyktingar med muslimsk bakgrund?

```{r NORDFORSK8_DV_C}

Source <- c('Strongly agree', 'Agree', 'Agree somewhat', 'Neither agree nor disagree', 'Disagree somewhat', 'Disagree', 'Strongly disagree', NA)
Iceland <- count(di_is, as_label(sp16))
Norway <- count(dn, as_label(r15pad_terror11postc)) %>% filter(`as_label(r15pad_terror11postc)` != 'Ikke spurt')
Sweden <- count(ds, as_label(q294)) 
NORDFORSK8_DV_C <- bind_cols(Source, Iceland, Norway, Sweden)

kable(NORDFORSK8_DV_C, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = sp16, Norway =  r15pad_terror11postc, Sweden = q294.")
```

