# EDUCATION



```{r EDUCATION_setup, include=FALSE, echo=FALSE}
if(!require("gt")){install.packages("gt");  library(gt)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("openxlsx")){install.packages("openxlsx");  library(openxlsx)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("sjlabelled")){install.packages("sjlabelled");  library(sjlabelled)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}
if(!require("webshot")){install.packages("webshot");  library(webshot)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```


```{r EDUCATION_PRE}
Pooled <- rep(1:13)
Iceland <- count(di, as_label(menntun)) %>% add_row(`as_label(menntun)` = NA, n=NA) %>% add_row(`as_label(menntun)` = NA, n=NA) %>% add_row(`as_label(menntun)` = NA, n=NA) %>% add_row(`as_label(menntun)` = NA, n=NA)
Norway <- count(dn, as_label(r15P4_2)) %>% filter(`as_label(r15P4_2)` != 'Ikke spurt')
Sweden <- count(ds, as_label(edu_mp36)) %>% add_row(`as_label(edu_mp36)` = NA, n=NA) %>% add_row(`as_label(edu_mp36)` = NA, n=NA) %>% add_row(`as_label(edu_mp36)` = NA, n=NA)
EDUCATION <- bind_cols(Pooled, Iceland, Norway, Sweden)

kable(EDUCATION, booktabs = T, linesep = "", escape = F, caption = "Panel variable names and values",  col.names = linebreak(c("Pooled", "Iceland", 'n', "Norway", 'n', "Sweden", 'n'))) %>%
  footnote(general = "Variable names. Iceland = menntun, Norway =  r15P4_2, Sweden = edu_mp36")
```

How to pool the education variable depends upon the research need of the project members.
The preliminary recoding (which will stand unless someone suggests another one) proposes to recode into a binary variable with high/low education levels.
The proposed cutoff for higher education levels in Iceland is 5 and higher, in Norway 6 and higher, and in Sweden 7 and higher.
