--- 
title: "Survey Guide: The Challenge from Terrorism in the Nordic Countries"
author: ""
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is the guide to the survey on the challenge from terrorism in the Nordic countries, conducted in Iceland, Norway, and Sweden in 2018-2019. "
---
--- 
title: "Survey Guide: The Challenge from Terrorism in the Nordic Countries"
author: ""
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is the guide to the survey on the challenge from terrorism in the Nordic countries, conducted in Iceland, Norway, and Sweden in 2018-2019. "
---

# About 

This document is a guide to the survey of the research project *The challenge from terrorism in the Nordic countries*.
The project is a collaboration between Iceland, Norway, and Sweden, and funded by the Nordic Research Council (NORDFORSK).


<!--chapter:end:index.Rmd-->


# Iceland

Placeholder


## Additional variables 

<!--chapter:end:03-iceland.Rmd-->

# Norway

```{r nor_setup, include=FALSE, echo=FALSE}
if(!require("codebook")){install.packages("codebook");  library(codebook)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```

```{r nor_load_data}

de <- read_sav('C:\\Users/svein/Documents/nordforskdata/Norwegian Citizen Panel - wave 15 - EN.sav') 
de <- de %>% select(starts_with('r15pad_terror'))

dn <- read_sav('C:\\Users/svein/Documents/nordforskdata/Norwegian Citizen Panel - wave 15 - NO.sav') 
dn <- dn %>% select(starts_with('r15pad_terror'), r15P1, r15P4_2, r15P5_1) %>% filter(!is.na(r15pad_terror1_ran1))
```

## Additional variables 

A specific data set is not created for this project, but relevant variables can be selected from the full panel data set.
The project group will together determine which variables ought to be pooled across the three countries.

<!--chapter:end:04-norway.Rmd-->


# Sweden

Placeholder


## Additional variables 

<!--chapter:end:05-sweden.Rmd-->

# POOL DATASETS

```{r POOL_setup, include=FALSE, echo=FALSE}
if(!require("gt")){install.packages("gt");  library(gt)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("magick")){install.packages("magick");  library(magick)}
if(!require("openxlsx")){install.packages("openxlsx");  library(openxlsx)}
if(!require("readxl")){install.packages("readxl");  library(readxl)}
if(!require("sjlabelled")){install.packages("sjlabelled");  library(sjlabelled)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}
if(!require("webshot")){install.packages("webshot");  library(webshot)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", cache = FALSE, message = FALSE )
```


<!--chapter:end:06-pool.Rmd-->


# NORDFORSK1

Placeholder


## NORDFORSK1_TACTIC1
## NORDFORSK1_TARGET
## NORDFORSK1_CASUALTIES
## NORDFORSK1_TACTIC2
## NORDFORSK1_ADJECTIVE
## NORDFORSK1_SUBJECTIVE                     
## NORDFORSK1_MOTIVATION
## NORDFORSK1_DV_A
## NORDFORSK1_DV_B
### NORDFORSK1_DV_B_1
### NORDFORSK1_DV_B_2
### NORDFORSK1_DV_B_3
### NORDFORSK1_DV_B_4
### NORDFORSK1_DV_B_5
### NORDFORSK1_DV_B_6
### NORDFORSK1_DV_B_7

<!--chapter:end:07-nordforsk1.Rmd-->


# NORDFORSK2

Placeholder


## NORDFORSK2_OBJECT
## NORDFORSK_TENSE
## NORDFORSK_DV

<!--chapter:end:08-nordforsk2.Rmd-->


# NORDFORSK3

Placeholder



<!--chapter:end:09-nordforsk3.Rmd-->


# NORDFORSK4

Placeholder



<!--chapter:end:10-nordforsk4.Rmd-->


# NORDFORSK5

Placeholder



<!--chapter:end:11-nordforsk5.Rmd-->


# NORDFORSK6

Placeholder


## NORDFORSK6_1
## NORDFORSK6_2
## NORDFORSK6_3
## NORDFORSK6_4
## NORDFORSK6_5
## NORDFORSK6_6

<!--chapter:end:12-nordforsk6.Rmd-->


# NORDFORSK7

Placeholder


## NORDFORSK7_EVENT
## NORDFORSK7_DV

<!--chapter:end:13-nordforsk7.Rmd-->


# NORDFORSK8

Placeholder


## NORDFORSK8_PRE
## NORDFORSK8_TREAT
## NORDFORSK8_DV_A
## NORDFORSK8_DV_B
## NORDFORSK8_DV_C

<!--chapter:end:14-nordforsk8.Rmd-->


# GENDER

Placeholder



<!--chapter:end:16-gender.Rmd-->


# AGE

Placeholder



<!--chapter:end:17-age.Rmd-->


# EDUCATION

Placeholder



<!--chapter:end:18-education.Rmd-->

